### 2022-08-15 doc/src/DuoPLIC.tex

\textbf{%
Warning!
This draft specification is likely to change before being accepted as
standard by the {\RISCV} International Association.%
}
\bigskip

>>>>

\textbf{%
Warning!
This chapter is only a draft, and might change significantly before 
being accepted as standard by the {\RISCV} International Association.
It remains possible that the Duo-PLIC specification
will never become a ratified standard.%
}
\bigskip
